NUll check for flashr2

### 2017-10-11 analysis/nullcheck2.Rmd
Files commited by wflow_commit.

set.seed(99)
T = 1000
lambda_0 = rep(NA,T)
flash_rank_0= rep(1,T)
flash2_rank_0= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_0)
  lambda_0[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X,objtype = "l",
                     ash_para_l = list(nullweight = 1 ),
                     ash_para_f = list(nullweight = 1 ))
  if(sum(g1$EL) ==0 )  {flash2_rank_0[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_0[t] = 0}
}

set.seed(99)
T = 1000
lambda_1 = rep(NA,T)
flash_rank_1= rep(1,T)
flash2_rank_1= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  nu = rnorm(P, 0, (1)/(sqrt(P)))
  # index_nu = sample(seq(1:P),(P*0.95))
  # nu[index_nu] = 0
  Sigma_1 = Sigma_0 + nu %*% t(nu)
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_1)
  lambda_1[t] =  svd(X)$d[1]
  data = set_flash_data(X)
  g1= flash_r1(data,verbose=F)
  g2 = flashr::flash(X,objtype = "l",
                     ash_para_l = list(nullweight = 1 ),
                     ash_para_f = list(nullweight = 1 ))
  if(sum(g1$EL) ==0 )  {flash2_rank_1[t] = 0}
  if(sum(g2$l) ==0 )  {flash_rank_1[t] = 0}
}

lambda_1_0_0 = lambda_0[which(flash_rank_0 ==0)]
lambda_1_0_1 = lambda_0[which(flash_rank_0 ==1)]
lambda_2_0_0 = lambda_0[which(flash2_rank_0 ==0)]
lambda_2_0_1 = lambda_0[which(flash2_rank_0 ==1)]

lambda_1_1_0 = lambda_1[which(flash_rank_1 ==0)]
lambda_1_1_1 = lambda_1[which(flash_rank_1 ==1)]
lambda_2_1_0 = lambda_1[which(flash2_rank_1 ==0)]
lambda_2_1_1 = lambda_1[which(flash2_rank_1 ==1)]

```

@@

```{r}
library(ggplot2)
dat = data.frame(lambda = c(lambda_0,lambda_1), name = c(rep("null",length(lambda_0)), rep("alt", length(lambda_1)) ))
ggplot(dat,aes(x=lambda)) +
  geom_histogram(data=subset(dat,name == 'null'),fill = "red", alpha = 0.2) +
  geom_histogram(data=subset(dat,name == 'alt'),fill = "green", alpha = 0.2) 
```

* red: null
* green: alternative

### flashr

```{r}
library(ggplot2)
dat = data.frame(lambda = c(lambda_1_0_0,lambda_1_0_1,lambda_1_1_0,lambda_1_1_1), 
                 name = c(rep("null 0",length(lambda_1_0_0)),
                          rep("null 1",length(lambda_1_0_1)),
                          rep("alt 0",length(lambda_1_1_0)),
                          rep("alt 1",length(lambda_1_1_1))))
ggplot(dat,aes(x=lambda)) +
  geom_histogram(data=subset(dat,name == 'null 0'),fill = "red", alpha = 0.2) +
  geom_histogram(data=subset(dat,name == 'null 1'),fill = "black", alpha = 0.2) +
  geom_histogram(data=subset(dat,name == 'alt 0'),fill = "blue", alpha = 0.2) +
  geom_histogram(data=subset(dat,name == 'alt 1'),fill = "green", alpha = 0.2)

```

* red: null as rank 0
* black: null as rank 1
* blue: alternative as 0
* green: alternative as 1

### flashr2

```{r}
library(ggplot2)
dat2 = data.frame(lambda = c(lambda_2_0_0,lambda_2_0_1,lambda_2_1_0,lambda_2_1_1), 
                 name = c(rep("null 0",length(lambda_2_0_0)),
                          rep("null 1",length(lambda_2_0_1)),
                          rep("alt 0",length(lambda_2_1_0)),
                          rep("alt 1",length(lambda_2_1_1))))
ggplot(dat,aes(x=lambda)) +
  geom_histogram(data=subset(dat2,name == 'null 0'),fill = "red", alpha = 0.2) +
  geom_histogram(data=subset(dat2,name == 'null 1'),fill = "black", alpha = 0.2) +
  geom_histogram(data=subset(dat2,name == 'alt 0'),fill = "blue", alpha = 0.2) +
  geom_histogram(data=subset(dat2,name == 'alt 1'),fill = "green", alpha = 0.2)

```

* red: null as rank 0
* black: null as rank 1
* blue: alternative as 0
* green: alternative as 1

>>>>

@@

### dense case

set.seed(99)
T = 300
lambda_0 = rep(NA,T)
flash2_rank_0= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_0)
  X = X/sqrt(mean((X)^2))
  lambda_0[t] =  svd(X)$d[1]
  data =  flashr2::flash_set_data(X)
  g1= flashr2::flash_r1(data,verbose=F)
  if(sum(g1$EL) ==0 )  {flash2_rank_0[t] = 0}
}

set.seed(99)
lambda_1 = rep(NA,T)
flash2_rank_1= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  nu = rnorm(P, 0, (2)/(sqrt(P)))
  # index_nu = sample(seq(1:P),(P*0.95))
  # nu[index_nu] = 0
  Sigma_1 = Sigma_0 + nu %*% t(nu)
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_1)
  X = X/sqrt(mean((X)^2))
  lambda_1[t] =  svd(X)$d[1]
  data = flashr2::flash_set_data(X)
  g1= flashr2::flash_r1(data,verbose=F)
  if(sum(g1$EL) ==0 )  {flash2_rank_1[t] = 0}
}

lambda_0_0 = lambda_0[which(flash2_rank_0 ==0)]
lambda_0_1 = lambda_0[which(flash2_rank_0 ==1)]

lambda_1_0 = lambda_1[which(flash2_rank_1 ==0)]
lambda_1_1 = lambda_1[which(flash2_rank_1 ==1)]

simple_roc <- function(labels, scores){
  labels <- labels[order(scores, decreasing=TRUE)]
  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
}

lambda.roc = simple_roc(labels = c(rep(0,T),rep(1,T)),scores = c(lambda_0,lambda_1))
plot(lambda.roc$FPR,lambda.roc$TPR,type = "l",col = "black")
flash.roc = simple_roc(labels = c(rep(0,T),rep(1,T)),scores = c(flash2_rank_0,flash2_rank_1))
lines(flash.roc$FPR,flash.roc$TPR,type = "l",col = "red")
```

### sparse case

set.seed(99)
T = 300
lambda_0 = rep(NA,T)
flash2_rank_0= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_0)
  X = X/sqrt(mean((X)^2))
  lambda_0[t] =  svd(X)$d[1]
  data =  flashr2::flash_set_data(X)
  g1= flashr2::flash_r1(data,verbose=F)
  if(sum(g1$EL) ==0 )  {flash2_rank_0[t] = 0}
}

set.seed(99)
lambda_1 = rep(NA,T)
flash2_rank_1= rep(1,T)
for(t in 1:T){
  P = 300
  N = 100
  Sigma_0 = diag(rep(1,P))
  nu = rnorm(P, 0, (6)/(sqrt(P)))
  index_nu = sample(seq(1:P),(P*0.95))
  nu[index_nu] = 0
  Sigma_1 = Sigma_0 + nu %*% t(nu)
  X = mvrnorm(n = N,mu = rep(0,P), Sigma = Sigma_1)
  X = X/sqrt(mean((X)^2))
  lambda_1[t] =  svd(X)$d[1]
  data = flashr2::flash_set_data(X)
  g1= flashr2::flash_r1(data,verbose=F)
  if(sum(g1$EL) ==0 )  {flash2_rank_1[t] = 0}
}

lambda_0_0 = lambda_0[which(flash2_rank_0 ==0)]
lambda_0_1 = lambda_0[which(flash2_rank_0 ==1)]

lambda_1_0 = lambda_1[which(flash2_rank_1 ==0)]
lambda_1_1 = lambda_1[which(flash2_rank_1 ==1)]

simple_roc <- function(labels, scores){
  labels <- labels[order(scores, decreasing=TRUE)]
  data.frame(TPR=cumsum(labels)/sum(labels), FPR=cumsum(!labels)/sum(!labels), labels)
}

lambda.roc = simple_roc(labels = c(rep(0,T),rep(1,T)),scores = c(lambda_0,lambda_1))
plot(lambda.roc$FPR,lambda.roc$TPR,type = "l",col = "black")
flash.roc = simple_roc(labels = c(rep(0,T),rep(1,T)),scores = c(flash2_rank_0,flash2_rank_1))
lines(flash.roc$FPR,flash.roc$TPR,type = "l",col = "red")
```

## likelihood ratio
